A Privacy Aware Mobile Sensor Application

### 2015-06-11 paper.tex
rescaled vul. graphic
'save harbor' -> 'safe harbor' 'Pricacy' -> 'Privacy'

\subsection{Privacy and Self Data Protection}
1890, the American politician Louis Brandis had specified privacy as the right to be left alone \cite{WarrenBrandeis:RightToPrivacy}. From the data processing point of view, this right is best expressed by the absence of information about a person in the mind of others. Indeed, this principle of “data minimization” is still fundamental to modern data protection legislation. The modern principles of data protection are codified by many legal systems in different countries, especially in Europe \cite{EU-directive2}, and by the US save harbor principles. However, modern data protection is more than only the absence of personal data. It is based on the personal right on self-determination over information and communication \cite{BVerfG:census}. This is, for example, very well expressed by Fried’s definition of 1970:
\begin{quote}
	Privacy is not simply an absence of information about us in the minds of others; rather it is the control we have over information about ourselves. \cite{CFried:Privacy}
\end{quote}
In order to realize this requirement in the modern IT world users are provided with user control functions, for example to decide about the access on their data for future use, and to view, modify, and delete unwanted data that had been collected. In its fundamental decision of May 13, 2014, the European Court has convicted Google to accept user demands to delete links to incorrect or irrelevant personal data in the Internet (C-131/12 – Google Spain SL). Such functions would constitute a so-called self-data-protection. It requires users to be highly aware of their rights and how to use them. Complementary, system-data-protection puts the load of data protection enforcement on the data collectors, ideally even without bothering the users. Typical system data protection functions are the deletion of personal data that are not bound to service purpose, the anonymization of personal data for research, and the abstinence from forwarding personal data to third parties. Together, system-data-protection and self-data-protection are supposed to provide a fair balance between the interests of service providers and their users.
In our research work we focus on self-data-protection according to Fried’s user control requirement \cite{CFried:Privacy}. A system data protection point of view would lead to other results, namely to a set of obligations for service providers. This is subject to further research.

@@

\begin{figure}
\newcommand{\tcell}[1]{\parbox[c][2cm]{4cm}{\vspace{3mm}#1\vspace{3mm}}}
\newcommand{\thead}[1]{\tcell{\Large\centering\textbf{#1}}}
\newcommand{\tbody}[1]{\tcell{\Large\centering #1}}
\centering
\resizebox{\textwidth}{!}{
\begin{tabular}{|c||c|c|c|c|c|c|c|}
\hline
& \thead{Pricacy of the Person}
& \thead{Pricacy of Behaviour and Action}
& \thead{Pricacy of Communication}
& \thead{Pricacy of Data and Image}
& \thead{Pricacy of Thoughts and Feelings}
& \thead{Pricacy of Location and Space}
& \thead{Pricacy of Association}
\\\hline\hline
\thead{GPS Sensor}
& \tbody{0.5} % Pricacy of the Person
& \tbody{0.5} % Pricacy of Behaviour and Action
& \tbody{0} % Pricacy of Communication
& \tbody{1} % Pricacy of Data and Image
& \tbody{0} % Pricacy of Thoughts and Feelings
& \tbody{1} % Pricacy of Location and Space
& \tbody{0.5} % Pricacy of Association
\\\hline
\thead{Motion Sensors}
& \tbody{1} % Pricacy of the Person
& \tbody{0.5} % Pricacy of Behaviour and Action
& \tbody{0} % Pricacy of Communication
& \tbody{1} % Pricacy of Data and Image
& \tbody{0} % Pricacy of Thoughts and Feelings
& \tbody{0} % Pricacy of Location and Space
& \tbody{0} % Pricacy of Association
\\\hline
\thead{Networking Sensors}
& \tbody{0.5} % Pricacy of the Person
& \tbody{0.5} % Pricacy of Behaviour and Action
& \tbody{0} % Pricacy of Communication
& \tbody{1} % Pricacy of Data and Image
& \tbody{0} % Pricacy of Thoughts and Feelings
& \tbody{1} % Pricacy of Location and Space
& \tbody{1} % Pricacy of Association
\\\hline
%\thead{HAR}
%& \tbody{-} % Pricacy of the Person
%& \tbody{-} % Pricacy of Behaviour and Action
%& \tbody{-} % Pricacy of Communication
%& \tbody{-} % Pricacy of Data and Image
%& \tbody{-} % Pricacy of Thoughts and Feelings
%& \tbody{-} % Pricacy of Location and Space
%& \tbody{-} % Pricacy of Association
%\\\hline
%\thead{SLD}
%& \tbody{-} % Pricacy of the Person
%& \tbody{-} % Pricacy of Behaviour and Action
%& \tbody{-} % Pricacy of Communication
%& \tbody{-} % Pricacy of Data and Image
%& \tbody{-} % Pricacy of Thoughts and Feelings
%& \tbody{-} % Pricacy of Location and Space
%& \tbody{-} % Pricacy of Association
%\\\hline
\end{tabular}
}
\newline
\newline
{\scriptsize 
0: No Impact,
0.5: Indirect Impact,
1: Direct Impact}
\caption{Sensor Data Privacy Impact Matrix}
\label{figure:Sensor Data Privacy Impact Matrix}
\end{figure}

@@

%input{./figures/LG-Vulnerabilities}
\begin{figure}
\centering
\includegraphics[width=0.6\textwidth]{diagrams/png/vulnerabilities.png}

>>>>

\subsection{Privacy and Self Data Protection}
1890, the American politician Louis Brandis had specified privacy as the right to be left alone \cite{WarrenBrandeis:RightToPrivacy}. From the data processing point of view, this right is best expressed by the absence of information about a person in the mind of others. Indeed, this principle of “data minimization” is still fundamental to modern data protection legislation. The modern principles of data protection are codified by many legal systems in different countries, especially in Europe \cite{EU-directive2}, and by the US safe harbor principles. However, modern data protection is more than only the absence of personal data. It is based on the personal right on self-determination over information and communication \cite{BVerfG:census}. This is, for example, very well expressed by Fried’s definition of 1970:
\begin{quote}
	Privacy is not simply an absence of information about us in the minds of others; rather it is the control we have over information about ourselves. \cite{CFried:Privacy}
\end{quote}
In order to realize this requirement in the modern IT world users are provided with user control functions, for example to decide about the access on their data for future use, and to view, modify, and delete unwanted data that had been collected. In its fundamental decision of May 13, 2014, the European Court has convicted Google to accept user demands to delete links to incorrect or irrelevant personal data in the Internet (C-131/12 – Google Spain SL). Such functions would constitute a so-called self-data-protection. It requires users to be highly aware of their rights and how to use them. Complementary, system-data-protection puts the load of data protection enforcement on the data collectors, ideally even without bothering the users. Typical system data protection functions are the deletion of personal data that are not bound to service purpose, the anonymization of personal data for research, and the abstinence from forwarding personal data to third parties. Together, system-data-protection and self-data-protection are supposed to provide a fair balance between the interests of service providers and their users.
In our research work we focus on self-data-protection according to Fried’s user control requirement \cite{CFried:Privacy}. A system data protection point of view would lead to other results, namely to a set of obligations for service providers. This is subject to further research.

@@

\begin{figure}
\newcommand{\tcell}[1]{\parbox[c][2cm]{4cm}{\vspace{3mm}#1\vspace{3mm}}}
\newcommand{\thead}[1]{\tcell{\Large\centering\textbf{#1}}}
\newcommand{\tbody}[1]{\tcell{\Large\centering #1}}
\centering
\resizebox{\textwidth}{!}{
\begin{tabular}{|c||c|c|c|c|c|c|c|}
\hline
& \thead{Privacy of the Person}
& \thead{Privacy of Behaviour and Action}
& \thead{Privacy of Communication}
& \thead{Privacy of Data and Image}
& \thead{Privacy of Thoughts and Feelings}
& \thead{Privacy of Location and Space}
& \thead{Privacy of Association}
\\\hline\hline
\thead{GPS Sensor}
& \tbody{0.5} % Privacy of the Person
& \tbody{0.5} % Privacy of Behaviour and Action
& \tbody{0} % Privacy of Communication
& \tbody{1} % Privacy of Data and Image
& \tbody{0} % Privacy of Thoughts and Feelings
& \tbody{1} % Privacy of Location and Space
& \tbody{0.5} % Privacy of Association
\\\hline
\thead{Motion Sensors}
& \tbody{1} % Privacy of the Person
& \tbody{0.5} % Privacy of Behaviour and Action
& \tbody{0} % Privacy of Communication
& \tbody{1} % Privacy of Data and Image
& \tbody{0} % Privacy of Thoughts and Feelings
& \tbody{0} % Privacy of Location and Space
& \tbody{0} % Privacy of Association
\\\hline
\thead{Networking Sensors}
& \tbody{0.5} % Pricacy of the Person
& \tbody{0.5} % Pricacy of Behaviour and Action
& \tbody{0} % Pricacy of Communication
& \tbody{1} % Pricacy of Data and Image
& \tbody{0} % Pricacy of Thoughts and Feelings
& \tbody{1} % Pricacy of Location and Space
& \tbody{1} % Pricacy of Association
\\\hline
%\thead{HAR}
%& \tbody{-} % Pricacy of the Person
%& \tbody{-} % Pricacy of Behaviour and Action
%& \tbody{-} % Pricacy of Communication
%& \tbody{-} % Pricacy of Data and Image
%& \tbody{-} % Pricacy of Thoughts and Feelings
%& \tbody{-} % Pricacy of Location and Space
%& \tbody{-} % Pricacy of Association
%\\\hline
%\thead{SLD}
%& \tbody{-} % Pricacy of the Person
%& \tbody{-} % Pricacy of Behaviour and Action
%& \tbody{-} % Pricacy of Communication
%& \tbody{-} % Pricacy of Data and Image
%& \tbody{-} % Pricacy of Thoughts and Feelings
%& \tbody{-} % Pricacy of Location and Space
%& \tbody{-} % Pricacy of Association
%\\\hline
\end{tabular}
}
\newline
\newline
{\scriptsize 
0: No Impact,
0.5: Indirect Impact,
1: Direct Impact}
\caption{Sensor Data Privacy Impact Matrix}
\label{figure:Sensor Data Privacy Impact Matrix}
\end{figure}

@@

%input{./figures/LG-Vulnerabilities}
\begin{figure}
\centering
\includegraphics[width=\textwidth]{diagrams/png/vulnerabilities.png}
